Methods and Results

### 2022-10-06 ms.Rmd
Added supp table

@@

>>>>

 coefs_lnSD <- coef(model1_lnSD)
 ci.lb_lnSD <- model1_lnSD$ci.lb
 ci.ub_lnSD <- model1_lnSD$ci.ub
 randef <- confint(model1_lnSD)

  table_fixed <- data.frame( Parameter = c("Intercept", "Treatment (Control)", "ln Mean", ""), 
                            Estimates = c(coefs_lnSD, ""),
                       `Upper 95% CI` = c(ci.ub_lnSD, ""),
                       `Lower 95% CI` = c(ci.lb_lnSD, ""), check.names = FALSE, row.names = NULL)

dat <- data.frame()

  for(i in 1:(length(randef)-1)){
    tmp <- randef[[i]][1]$random[1,]
    dat <- rbind(dat, tmp)
  }
  names(dat) <- c("est", "lb", "up")

  table_rand <- data.frame(     Parameter = c("Study", "Residual", "Species", "tau^2", "rho"), 
                                Estimates = dat$est, 
                           `Upper 95% CI` = dat$lb,
                           `Lower 95% CI` = dat$up,check.names = FALSE, row.names = NULL)
```

@@

```{r, tables1, tab.cap = "Multi-level meta-regression model with log standard deviation (lnSD)"}
flextable(rbind(table_fixed,table_rand)) %>% 
      add_header_row(values = "Fixed Effects", colwidths = 3) %>% 
      bold(part = "header", i = 1) %>% 
      width(j = c(2,3,4), width = c(5, 2, 2)) %>%
      align(align = "center", part = "all") %>% 
      compose(i = 4, j = 3, value = as_paragraph(as_b("Random Effects")))
